---
title: "Behavioral CV Simulation"
author: "Gregy Gustavo Tuerah"
date: "2025-04-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tibble)
library(purrr)
library(tidyr)
library(ggplot2)
library(numDeriv)
library(knitr)
```
```{r}
# Action 1: Simulate four moments at benchmark parameter values for p and v, but with s = 0

cv_treatments <- expand.grid(tau = c(20, 50),
                              p = c(0.001, 0.02)) # note --> imagine its 2 x 2 now

simulate_cv_moments <- function(mu_v, sigma_v, N_per_cell = 100000) { # this function is the main function I got from the help of ChatGPT4o
  cv_results <- numeric(nrow(cv_treatments))
  
  for (i in seq_len(nrow(cv_treatments))) { # making sure the function is for every component
    treat <- cv_treatments[i, ]
    
    p <- treat$p
    tau <- treat$tau
    
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v)
    
    # s = 0, I = 0 --> remember from the question we have this assumption
    score <- p * (v - tau) # the model
    Y <- as.integer(score > 0) # the outcome probability voting yes
    
    cv_results[i] <- mean(Y)
  }
  return(cv_results)
}

# Simulated results
simulated <- simulate_cv_moments(mu_v = 40, sigma_v = 50)

# Analytical results
analytical <- 1 - pnorm(cv_treatments$tau, mean = 40, sd = 50) # finding it manually

# Put the information into the table
results_table <- data.frame(
  Treatment = c("{pl, Tl}", "{pl, Th}", "{ph, Tl}", "{ph, Th}"), # Treatment parameters used
  p = cv_treatments$p,
  tau = cv_treatments$tau,
  Simulated = round(simulated, 5),
  Analytical = round(analytical, 5)
)

kable(results_table, caption = "Simulated and Analytical Moments for CV Action 1")
```
```{r, warning=FALSE}

benchmark_theta <- list( # benchmark values are given
  mu_v = 40,
  sigma_v = 50,
  mu_s = 0,
  sigma_s = 2
) # This code will be used many times

# I will use the same function I made before

simulate_cv_moments <- function(mu_v, sigma_v, N_per_cell = 100000) {
  cv_treatments <- expand.grid(tau = c(20, 50), p = c(0.001, 0.02)) # include the cv_treatments to the function directly
  cv_results <- numeric(nrow(cv_treatments)) # make sure we have storage for the results
  
  for (i in seq_len(nrow(cv_treatments))) { # doing this across each treatment
    treat <- cv_treatments[i, ]
    p <- treat$p
    tau <- treat$tau
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v) # draw v
    score <- p * (v - tau)
    Y <- as.integer(score > 0)
    cv_results[i] <- mean(Y) # put the result in the storage
  }
  return(cv_results)
}

compare_parameter <- function(param_name, grid_values, benchmark_theta, N_per_cell = 100000) { # this is the second function I got help with
  # I claim that this function will vary one parameter at a time and the others at their benchmark
  map_dfr(grid_values, function(val) { # bind into one data frame
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    # below is the simulations based on the theta we have
    sims <- simulate_cv_moments(mu_v = theta$mu_v, sigma_v = theta$sigma_v, N_per_cell)
    
    tibble( # making the parameter into a table
      parameter = param_name,
      param_value = val,  
      `{pl, Tl}` = sims[1],
      `{pl, Th}` = sims[2],
      `{ph, Tl}` = sims[3],
      `{ph, Th}` = sims[4]
    )
  })
}

# Define grids for each parameter
param_grids <- list(
  mu_v = seq(20, 60, by = 2),
  sigma_v = seq(20, 100, by = 5)
)

# Run comparisons and combine into one tidy data frame
all_results <- bind_rows(
  compare_parameter("mu_v", param_grids$mu_v, benchmark_theta),
  compare_parameter("sigma_v", param_grids$sigma_v, benchmark_theta)
)

plot_comparative_statics <- function(results_df) { # ploting functions to show the comparative statics
  results_long <- results_df %>%
    pivot_longer(cols = starts_with("{"), names_to = "moment", values_to = "moment_value") # we change the matrix into long
  
  ggplot(results_long, aes(x = param_value, y = moment_value, color = moment)) +
    geom_line(size = 1.2) + # plot the moment as a line
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on Moments",
         x = "Parameter Value",
         y = "Simulated Moment Value") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

plot_comparative_statics(all_results)

```
```{r}
# Repeat the same code above
simulate_cv_moments_pflex <- function(mu_v, sigma_v, p_l, p_h, N_per_cell = 100000) {
  cv_treatments <- expand.grid(tau = c(20, 50), p_label = c("pl", "ph"))
  cv_results <- numeric(nrow(cv_treatments))
  
  for (i in seq_len(nrow(cv_treatments))) {
    treat <- cv_treatments[i, ]
    
    p <- if (treat$p_label == "pl") p_l else p_h
    tau <- treat$tau
    
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v)
    score <- p * (v - tau)
    Y <- as.integer(score > 0)
    
    cv_results[i] <- mean(Y)
  }
  return(cv_results)
}

compare_pl_or_ph <- function(param_name, grid_values, benchmark_theta, N_per_cell = 100000) {
  map_dfr(grid_values, function(val) {
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    sims <- simulate_cv_moments_pflex(
      mu_v = theta$mu_v,
      sigma_v = theta$sigma_v,
      p_l = theta$p_l,
      p_h = theta$p_h,
      N_per_cell = N_per_cell
    )
    
    tibble(
      parameter = param_name,
      param_value = val,
      `{pl, Tl}` = sims[1],
      `{pl, Th}` = sims[2],
      `{ph, Tl}` = sims[3],
      `{ph, Th}` = sims[4]
    )
  })
}

benchmark_theta <- list(
  mu_v = 40,
  sigma_v = 50,
  p_l = 0.001,
  p_h = 0.02
)

results_pl <- compare_pl_or_ph("p_l", seq(0.0005, 0.005, by = 0.0005), benchmark_theta)
results_ph <- compare_pl_or_ph("p_h", seq(0.01, 0.05, by = 0.005), benchmark_theta)

all_results <- bind_rows(results_pl, results_ph)

plot_comparative_statics <- function(results_df) {
  results_long <- results_df %>%
    pivot_longer(cols = starts_with("{"), names_to = "moment", values_to = "moment_value")
  
  ggplot(results_long, aes(x = param_value, y = moment_value, color = moment)) +
    geom_line(size = 1.2) +
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on Moments",
         x = "Parameter Value",
         y = "Simulated Moment Value") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

plot_comparative_statics(all_results)
```
```{r}
empirical_moments <- simulate_cv_moments(mu_v = 40, sigma_v = 50)

# The code below will also be used again

gmm_objective <- function(theta) { # define the GMM based on the lecture notes 
  mu_v <- theta[1]
  sigma_v <- theta[2]
  p_l <- theta[3]
  p_h <- theta[4]
  
  
  simulated <- simulate_cv_moments_pflex(mu_v, sigma_v, p_l, p_h)
  
  loss <- sum((simulated - empirical_moments)^2)
  return(loss)
}

# I will then choosing the starting values -- as recommended
# Starting values (somewhat off from truth to test identification)
theta_start <- c(mu_v = 30, sigma_v = 70, p_l = 0.005, p_h = 0.01)

result <- optim(
  par = theta_start,
  fn = gmm_objective,
  method = "L-BFGS-B",
  control = list(maxit = 100000)
)

print(result$par)       # Estimated parameters
print(result$value)     # Objective function value (how close we got)

# - > Plot this to see it better

estimated_theta <- result$par

simulated_estimated <- simulate_cv_moments_pflex(
  mu_v = estimated_theta["mu_v"],
  sigma_v = estimated_theta["sigma_v"],
  p_l = estimated_theta["p_l"],
  p_h = estimated_theta["p_h"]
)

moment_names <- c("{pl, Tl}", "{pl, Th}", "{ph, Tl}", "{ph, Th}")

df_plot <- tibble(
  Treatment = moment_names,
  Empirical = empirical_moments,
  Estimated = simulated_estimated
) %>%
  pivot_longer(cols = c(Empirical, Estimated), names_to = "Source", values_to = "Moment")

ggplot(df_plot, aes(x = Treatment, y = Moment, fill = Source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Empirical vs. Estimated Moments",
       y = "Moment Value", x = "Treatment Cell") +
  theme_minimal()

```
```{r}
# First I will try to simulate the and measure the comparative statics

# Comparing parameter v

simulate_cv_moments_with_s <- function(mu_v, sigma_v, p_l, p_h, mu_s, sigma_s, N_per_cell = 100000) {
  cv_treatments <- expand.grid(tau = c(20, 50), p_label = c("pl", "ph"))
  cv_results <- numeric(nrow(cv_treatments))
  
  for (i in seq_len(nrow(cv_treatments))) {
    treat <- cv_treatments[i, ]
    
    p <- if (treat$p_label == "pl") p_l else p_h
    tau <- treat$tau
    
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v)
    s <- rnorm(N_per_cell, mean = mu_s, sd = sigma_s)
    
    score <- p * (v - tau) + s
    Y <- as.integer(score > 0)
    
    cv_results[i] <- mean(Y)
  }
  return(cv_results)
}

empirical_moments <- simulate_cv_moments_with_s(
  mu_v = 40,
  sigma_v = 50,
  p_l = 0.001,
  p_h = 0.02,
  mu_s = 1,
  sigma_s = 2
)

benchmark_theta <- list(
  mu_v = 40,
  sigma_v = 50,
  p_l = 0.001,
  p_h = 0.02,
  mu_s = 1,
  sigma_s = 2
)

compare_parameter_v <- function(param_name, grid_values, benchmark_theta, N_per_cell = 100000) {
  map_dfr(grid_values, function(val) {
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    sims <- simulate_cv_moments_with_s(
      mu_v = theta$mu_v,
      sigma_v = theta$sigma_v,
      p_l = theta$p_l,
      p_h = theta$p_h,
      mu_s = theta$mu_s,
      sigma_s = theta$sigma_s,
      N_per_cell = N_per_cell
    )
    
    tibble(
      parameter = param_name,
      param_value = val,
      `{pl, Tl}` = sims[1],
      `{pl, Th}` = sims[2],
      `{ph, Tl}` = sims[3],
      `{ph, Th}` = sims[4]
    )
  })
}

# Grid for v
param_grids_v <- list(
  mu_v = seq(20, 60, by = 2),
  sigma_v = seq(20, 100, by = 5)
)

# Run
all_results_v <- bind_rows(
  compare_parameter_v("mu_v", param_grids_v$mu_v, benchmark_theta),
  compare_parameter_v("sigma_v", param_grids_v$sigma_v, benchmark_theta)
)

plot_comparative_results <- function(results_df) {
  results_long <- results_df %>%
    pivot_longer(cols = starts_with("{"), names_to = "moment", values_to = "moment_value")
  
  ggplot(results_long, aes(x = param_value, y = moment_value, color = moment)) +
    geom_line(size = 1.2) +
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on Moments",
         x = "Parameter Value",
         y = "Simulated Moment Value") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

# Then plot each
plot_comparative_results(all_results_v)

# - # - # - # - #

# Compare parameter p
compare_parameter_p <- function(param_name, grid_values, benchmark_theta, N_per_cell = 100000) {
  map_dfr(grid_values, function(val) {
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    sims <- simulate_cv_moments_with_s(
      mu_v = theta$mu_v,
      sigma_v = theta$sigma_v,
      p_l = theta$p_l,
      p_h = theta$p_h,
      mu_s = theta$mu_s,
      sigma_s = theta$sigma_s,
      N_per_cell = N_per_cell
    )
    
    tibble(
      parameter = param_name,
      param_value = val,
      `{pl, Tl}` = sims[1],
      `{pl, Th}` = sims[2],
      `{ph, Tl}` = sims[3],
      `{ph, Th}` = sims[4]
    )
  })
}

# Grid for p
param_grids_p <- list(
  p_l = seq(0.0005, 0.005, by = 0.0005),
  p_h = seq(0.01, 0.05, by = 0.005)
)

# Run
all_results_p <- bind_rows(
  compare_parameter_p("p_l", param_grids_p$p_l, benchmark_theta),
  compare_parameter_p("p_h", param_grids_p$p_h, benchmark_theta)
)

plot_comparative_results(all_results_p)

# - # - # - # - #
# Compare parameter s
compare_parameter_s <- function(param_name, grid_values, benchmark_theta, N_per_cell = 100000) {
  map_dfr(grid_values, function(val) {
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    sims <- simulate_cv_moments_with_s(
      mu_v = theta$mu_v,
      sigma_v = theta$sigma_v,
      p_l = theta$p_l,
      p_h = theta$p_h,
      mu_s = theta$mu_s,
      sigma_s = theta$sigma_s,
      N_per_cell = N_per_cell
    )
    
    tibble(
      parameter = param_name,
      param_value = val,
      `{pl, Tl}` = sims[1],
      `{pl, Th}` = sims[2],
      `{ph, Tl}` = sims[3],
      `{ph, Th}` = sims[4]
    )
  })
}

# Grid for s
param_grids_s <- list(
  mu_s = seq(-1, 3, by = 0.5),
  sigma_s = seq(1, 5, by = 0.5)
)

# Run
all_results_s <- bind_rows(
  compare_parameter_s("mu_s", param_grids_s$mu_s, benchmark_theta),
  compare_parameter_s("sigma_s", param_grids_s$sigma_s, benchmark_theta)
)

plot_comparative_statics <- function(results_df) {
  results_long <- results_df %>%
    pivot_longer(cols = starts_with("{"), names_to = "moment", values_to = "moment_value")
  
  ggplot(results_long, aes(x = param_value, y = moment_value, color = moment)) +
    geom_line(size = 1.2) +
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on Moments",
         x = "Parameter Value",
         y = "Simulated Moment Value") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

plot_comparative_statics <- function(results_df) {
  results_long <- results_df %>%
    pivot_longer(cols = starts_with("{"), names_to = "moment", values_to = "moment_value")
  
  ggplot(results_long, aes(x = param_value, y = moment_value, color = moment)) +
    geom_line(size = 1.2) +
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on Moments",
         x = "Parameter Value",
         y = "Simulated Moment Value") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

plot_comparative_results(all_results_s)
```

Now let's try to estimate the parameters, although I know, we cannot get the exact value due to the mismatch of moments and parameters interest.
```{r}

gmm_objective_6param <- function(theta) {
  mu_v <- theta[1]
  sigma_v <- theta[2]
  p_l <- theta[3]
  p_h <- theta[4]
  mu_s <- theta[5]
  sigma_s <- theta[6]
  
  simulated <- simulate_cv_moments_with_s(
    mu_v = mu_v,
    sigma_v = sigma_v,
    p_l = p_l,
    p_h = p_h,
    mu_s = mu_s,
    sigma_s = sigma_s
  )
  
  loss <- sum((simulated - empirical_moments)^2)
  return(loss)
}

theta_start <- c(mu_v = 30, sigma_v = 70, p_l = 0.005, p_h = 0.01, mu_s = 0.5, sigma_s = 3)

result_6param <- optim(
  par = theta_start,
  fn = gmm_objective_6param,
  method = "L-BFGS-B",
  control = list(maxit = 100000)
)

# Checking the optimization convergence:
result_6param$convergence # if its 0, then I did it

# Print results
print(result_6param$par)     # Estimated parameters
print(result_6param$value)   # Objective function value
```

```{r}
gmm_objective_2param <- function(theta) {
  mu_v <- theta[1]
  sigma_v <- theta[2]
  
  # Fixed known parameters
  p_l <- 0.001
  p_h <- 0.02
  mu_s <- 1
  sigma_s <- 2
  
  simulated <- simulate_cv_moments_with_s(
    mu_v = mu_v,
    sigma_v = sigma_v,
    p_l = p_l,
    p_h = p_h,
    mu_s = mu_s,
    sigma_s = sigma_s
  )
  
  loss <- sum((simulated - empirical_moments)^2)
  return(loss)
}

theta_start_2param <- c(mu_v = 30, sigma_v = 70)

result_2param <- optim(
  par = theta_start_2param,
  fn = gmm_objective_2param,
  method = "L-BFGS-B",
  control = list(maxit = 100000)
)

# Checking convergence
print(result_2param$convergence) # Should be 0
# Print estimated parameters
print(result_2param$par)
# Print objective value
print(result_2param$value)

# Plot
# Get estimated parameters
estimated_theta_2param <- result_2param$par

# Simulate using estimated parameters
simulated_estimated_2param <- simulate_cv_moments_with_s(
  mu_v = estimated_theta_2param["mu_v"],
  sigma_v = estimated_theta_2param["sigma_v"],
  p_l = 0.001,
  p_h = 0.02,
  mu_s = 1,
  sigma_s = 2
)

# Prepare data for plotting
df_plot_2param <- tibble(
  Treatment = moment_names,
  Empirical = empirical_moments,
  Estimated = simulated_estimated_2param
) %>%
  pivot_longer(cols = c(Empirical, Estimated), names_to = "Source", values_to = "Moment")

# Plot
ggplot(df_plot_2param, aes(x = Treatment, y = Moment, fill = Source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Empirical vs. Estimated Moments (Fixing $p$ and $s$)",
       y = "Moment Value", x = "Treatment Cell") +
  theme_minimal()
```
```{r, warning=FALSE}
# For the full model that includes all treatment arms

full_treatments <- expand.grid(
  tau = c(20, 50),            # low, high tax
  p_label = c("pl", "ph"),     # low, high consequentiality
  I_label = c("yes", "none", "no") # incentive to say yes, none, or no
)

# Simulation function that includes incentives I
simulate_full_moments <- function(mu_v, sigma_v, p_l, p_h, mu_s, sigma_s, incentive_strength = 0.5, N_per_cell = 100000) {
  full_results <- numeric(nrow(full_treatments))
  
  for (i in seq_len(nrow(full_treatments))) {
    treat <- full_treatments[i, ]
    
    # Set treatment-specific parameters
    p <- if (treat$p_label == "pl") p_l else p_h
    tau <- treat$tau
    I_sign <- switch(treat$I_label,
                     "yes" = 1,
                     "none" = 0,
                     "no" = -1)
    
    # Draw random variables
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v)
    s <- rnorm(N_per_cell, mean = mu_s, sd = sigma_s)
    
    # Now incentive random draw
    I <- incentive_strength * I_sign
    
    # Compute score and decision
    score <- p * (v - tau) + s + I
    Y <- as.integer(score > 0)
    
    # Save the share voting "Yes"
    full_results[i] <- mean(Y)
  }
  return(full_results)
}

# Simulate with the benchmark parameter again

benchmark_theta_full <- list(
  mu_v = 40,
  sigma_v = 50,
  p_l = 0.001,
  p_h = 0.02,
  mu_s = 1,
  sigma_s = 2
)

empirical_moments_full <- simulate_full_moments(
  mu_v = benchmark_theta_full$mu_v,
  sigma_v = benchmark_theta_full$sigma_v,
  p_l = benchmark_theta_full$p_l,
  p_h = benchmark_theta_full$p_h,
  mu_s = benchmark_theta_full$mu_s,
  sigma_s = benchmark_theta_full$sigma_s
)

table_moments <- full_treatments %>%
  mutate(
    Moment = empirical_moments_full,
    Treatment_Label = paste0(
      "p:", p_label, ", tau:", tau, ", I:", I_label
    )
  ) %>%
  select(Treatment_Label, Moment)

kable(table_moments, caption = "Mapping of Treatment Cells to Empirical Moments")
```
```{r, warning=FALSE}
# First is the comparative statics

compare_parameter_full <- function(param_name, grid_values, benchmark_theta, incentive_strength = 0.5, N_per_cell = 100000) {
  map_dfr(grid_values, function(val) {
    theta <- benchmark_theta
    theta[[param_name]] <- val
    
    sims <- simulate_full_moments(
      mu_v = theta$mu_v,
      sigma_v = theta$sigma_v,
      p_l = theta$p_l,
      p_h = theta$p_h,
      mu_s = theta$mu_s,
      sigma_s = theta$sigma_s,
      incentive_strength = incentive_strength,
      N_per_cell = N_per_cell
    )
    
    sims_df <- tibble(Treatment = 1:12, Moment = sims)
    
    sims_df %>%
      mutate(
        parameter = param_name,
        param_value = val
      )
  })
}

param_grids_full <- list(
  p_l = seq(0.0005, 0.005, by = 0.0005),
  p_h = seq(0.01, 0.05, by = 0.005),
  mu_v = seq(20, 60, by = 5),
  sigma_v = seq(20, 100, by = 10),
  mu_s = seq(0, 2, by = 0.5),
  sigma_s = seq(1, 5, by = 0.5)
)

# Example for varying mu_v
results_mu_v <- compare_parameter_full("mu_v", param_grids_full$mu_v, benchmark_theta_full)

# Example for varying sigma_v
results_sigma_v <- compare_parameter_full("sigma_v", param_grids_full$sigma_v, benchmark_theta_full)

# Example for varying p_l
results_p_l <- compare_parameter_full("p_l", param_grids_full$p_l, benchmark_theta_full)

# Example for varying p_h
results_p_h <- compare_parameter_full("p_h", param_grids_full$p_h, benchmark_theta_full)

# Example for varying mu_s
results_mu_s <- compare_parameter_full("mu_s", param_grids_full$mu_s, benchmark_theta_full)

# Example for varying sigma_s
results_sigma_s <- compare_parameter_full("sigma_s", param_grids_full$sigma_s, benchmark_theta_full)

# Plot
plot_comparative_statics_full <- function(results_df) {
  results_df %>%
    ggplot(aes(x = param_value, y = Moment, color = as.factor(Treatment))) +
    geom_line(size = 1.2) +
    facet_wrap(~parameter, scales = "free_x") +
    labs(title = "Comparative Statics: Effect of Each Parameter on 12 Moments",
         x = "Parameter Value",
         y = "Moment Value",
         color = "Treatment") +
    theme_minimal() +
    theme(legend.position = "bottom")
}

plot_comparative_statics_full(results_mu_v)
plot_comparative_statics_full(results_sigma_v)
plot_comparative_statics_full(results_p_l)
plot_comparative_statics_full(results_p_h)
plot_comparative_statics_full(results_mu_s)
plot_comparative_statics_full(results_sigma_s)


```

```{r, warning=FALSE}
# Next is the estimation and optimization
gmm_objective_full <- function(theta) {
  mu_v <- theta[1]
  sigma_v <- theta[2]
  p_l <- theta[3]
  p_h <- theta[4]
  mu_s <- theta[5]
  sigma_s <- theta[6]
  
  simulated <- simulate_full_moments(
    mu_v = mu_v,
    sigma_v = sigma_v,
    p_l = p_l,
    p_h = p_h,
    mu_s = mu_s,
    sigma_s = sigma_s,
    incentive_strength = 0.5,
    N_per_cell = 100000
  )
  
  loss <- sum((simulated - empirical_moments_full)^2)
  return(loss)
}

theta_start_full <- c(
  mu_v = 30,
  sigma_v = 70,
  p_l = 0.005,
  p_h = 0.01,
  mu_s = 0.5,
  sigma_s = 3
)

result_full <- optim(
  par = theta_start_full,
  fn = gmm_objective_full,
  method = "L-BFGS-B",
  control = list(maxit = 100000)
)

print(result_full$convergence)  # Should be 0
print(result_full$par)           # Estimated parameters
print(result_full$value)         # Objective function value

# Plot
# Simulate with estimated parameters
estimated_theta_full <- result_full$par

simulated_estimated_full <- simulate_full_moments(
  mu_v = estimated_theta_full["mu_v"],
  sigma_v = estimated_theta_full["sigma_v"],
  p_l = estimated_theta_full["p_l"],
  p_h = estimated_theta_full["p_h"],
  mu_s = estimated_theta_full["mu_s"],
  sigma_s = estimated_theta_full["sigma_s"],
  incentive_strength = 0.5,
  N_per_cell = 100000
)

moment_names_full <- paste0("Treatment_", 1:12)

df_plot_full <- tibble(
  Treatment = moment_names_full,
  Empirical = empirical_moments_full,
  Estimated = simulated_estimated_full
) %>%
  pivot_longer(cols = c(Empirical, Estimated), names_to = "Source", values_to = "Moment")

# Plot
ggplot(df_plot_full, aes(x = Treatment, y = Moment, fill = Source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Empirical vs. Estimated Moments (Full Design)",
       y = "Moment Value", x = "Treatment Cell") +
  theme_minimal()
```

# This is the wrong model: simulate moments assuming s = 0
simulate_cv_moments_wrong <- function(mu_v, sigma_v, p_l, p_h, N_per_cell = 100000) {
  # But with 12 treatment combinations
  treatments <- expand.grid(
    tau = c(20, 50),
    p_label = c("pl", "ph"),
    I = c(-0.5, 0, 0.5)
  )
  
  results <- numeric(nrow(treatments))
  
  for (i in seq_len(nrow(treatments))) {
    treat <- treatments[i, ]
    
    p <- if (treat$p_label == "pl") p_l else p_h
    tau <- treat$tau
    incentive <- treat$I
    
    v <- rnorm(N_per_cell, mean = mu_v, sd = sigma_v)
    
    # the score now assume s = 0
    score <- p * (v - tau) + incentive
    Y <- as.integer(score > 0)
    
    results[i] <- mean(Y)
  }
  
  return(results)
}

gmm_objective_wrong <- function(theta) {
  mu_v <- theta[1]
  sigma_v <- theta[2]
  p_l <- theta[3]
  p_h <- theta[4]
  
  simulated_moments <- simulate_cv_moments_wrong(mu_v, sigma_v, p_l, p_h)
  
  loss <- sum((simulated_moments - empirical_moments_full)^2)
  return(loss)
}

theta_start_wrong <- c(mu_v = 30, sigma_v = 70, p_l = 0.005, p_h = 0.01)

result_wrong <- optim(
  par = theta_start_wrong,
  fn = gmm_objective_wrong,
  method = "L-BFGS-B",
  control = list(maxit = 100000)
)

print(result_wrong$par)     # Estimated parameters
print(result_wrong$value)   # Objective function value


# Simulate the estimation
simulated_estimated_wrong <- simulate_cv_moments_wrong(
  mu_v = result_wrong$par["mu_v"],
  sigma_v = result_wrong$par["sigma_v"],
  p_l = result_wrong$par["p_l"],
  p_h = result_wrong$par["p_h"]
)

treatment_labels <- paste0("Treatment_", 1:12)

df_plot_wrong <- tibble(
  Treatment = treatment_labels,
  Empirical = empirical_moments_full,
  Estimated = simulated_estimated_wrong
) %>%
  pivot_longer(cols = c(Empirical, Estimated), names_to = "Source", values_to = "Moment")

# Plot
ggplot(df_plot_wrong, aes(x = Treatment, y = Moment, fill = Source)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Empirical vs. Estimated Moments (Assuming $s=0$)",
       y = "Moment Value", x = "Treatment Cell") +
  theme_minimal()
```
```{r}
# In this setup, I simulate data for 1000 individuals 
# randomly assigned across the treatment arms (tau, p, incentive).
# Then I estimate the full model parameters and compute 
# standard errors based on empirical moment variability.

# Let's include all the benchmark values
benchmark_theta <- list(
  mu_v = 40,
  sigma_v = 50,
  mu_s = 1,
  sigma_s = 2,
  p_l = 0.001,
  p_h = 0.02
)

tau_values <- c(20, 50)
incentive_values <- c(-0.5, 0, 0.5)

# I claim we will do random assignment

set.seed(35650)

N <- 1000

simulated_data <- tibble(
  tau = sample(tau_values, N, replace = TRUE),
  p_label = sample(c("pl", "ph"), N, replace = TRUE),
  incentive = sample(incentive_values, N, replace = TRUE)
)

# In here I try to draw individual (v, s) based on distributions
simulated_data <- simulated_data %>%
  mutate(
    v = rnorm(N, mean = benchmark_theta$mu_v, sd = benchmark_theta$sigma_v),
    s = rnorm(N, mean = benchmark_theta$mu_s, sd = benchmark_theta$sigma_s),
    p = if_else(p_label == "pl", benchmark_theta$p_l, benchmark_theta$p_h),
    score = p * (v - tau) + s + incentive,
    Y = as.integer(score > 0) # 1 = Yes, 0 = No
  )

# Compute the empirical moments
empirical_moments <- simulated_data %>% # the average vote "Yes"
  group_by(tau, p_label, incentive) %>% # remember to still draw based on these three
  summarise(moment = mean(Y), .groups = "drop") %>%
  mutate(cell_id = row_number()) # 1 to 12

# Making the model-predicted moments
simulate_moments <- function(theta, data) {
  mu_v <- theta[1]
  sigma_v <- theta[2]
  p_l <- theta[3]
  p_h <- theta[4]
  mu_s <- theta[5]
  sigma_s <- theta[6]
  
  # For each treatment group, simulate expected Pr(Yes)
  predicted <- data %>%
    group_by(tau, p_label, incentive) %>%
    summarise(
      pred_moment = {
        p <- if_else(p_label == "pl", p_l, p_h)
        mean(pnorm(p * (mu_v - tau) + mu_s + incentive, mean = 0, sd = sqrt((p^2) * sigma_v^2 + sigma_s^2)))
      },
      .groups = "drop"
    ) %>%
    pull(pred_moment)
  
  return(predicted)
}

# Make the GMM function
gmm_objective <- function(theta, data, moments) {
  simulated <- simulate_moments(theta, data)
  sum((simulated - moments$moment)^2) # Squared distance
}

# Starting values
theta_start <- c(30, 70, 0.005, 0.01, 0, 1) 

result_full <- optim(
  par = theta_start,
  fn = gmm_objective,
  data = simulated_data,
  moments = empirical_moments,
  method = "L-BFGS-B",
  control = list(maxit = 10000)
)

theta_hat <- result_full$par

# Finding out the var-cov for the SE
cell_counts <- simulated_data %>%
  group_by(tau, p_label, incentive) %>%
  summarise(n = n(), .groups = "drop") %>%
  arrange(tau, p_label, incentive)

# Diagonal variance-covariance matrix
S_hat <- diag(empirical_moments$moment * (1 - empirical_moments$moment) / cell_counts$n)

jacobian <- jacobian(
  func = function(theta) simulate_moments(theta, simulated_data),
  x = theta_hat
)

# GMM Variance-Covariance matrix --> Standard errors
vcov_theta <- solve(t(jacobian) %*% jacobian) %*% (t(jacobian) %*% S_hat %*% jacobian) %*% solve(t(jacobian) %*% jacobian)
se_theta <- sqrt(diag(vcov_theta))

# Table
model_table <- tibble(
  Parameter = c("mu_v", "sigma_v", "p_l", "p_h", "mu_s", "sigma_s"),
  Estimate = theta_hat,
  Std_Error = se_theta
)

kable(model_table, caption = "Estimation Results with Standard Errors")
```










